---
title: "elastic net tuning Project"
author: "Erasmo Rivas"
date: "2022-12-04"
output: pdf_document
---

```{r}
yelp


```

```{r}
elastic_net_spec <- multinom_reg(penalty = tune(),
                                 mixture = tune()) %>% 
  set_mode("classification") %>% 
  set_engine("glmnet")

en_wkflow <- workflow() %>% 
  add_recipe(yelp_recipe) %>% 
  add_model(elastic_net_spec)

en_grid <- grid_regular(penalty(range = c(-5,5)),
                        mixture(range = c(0,1)),
                        levels = 10)
```



```{r}
tune_res <- tune_grid(
  en_wkflow,
  resamples = yelp_folds,
  grid = en_grid
)

```


```{r}
autoplot(tune_res)
```


```{r}
best_model <- select_best(tune_res, metric = "roc_auc")
en_final <- finalize_workflow(en_wkflow, best_model)

en_final_fit <- fit(en_final, data = yelp_train)


predicted_data <- augment(en_final_fit, new_data = yelp_test) %>% 
  select(stars, starts_with(".pred"))

```

```{r}
predicted_data %>% roc_auc(stars, .pred_1:.pred_5)


```

### Categories 

The <code>numCategories</code> is an integer which represent the number of distinct categories that a restaurant may fall under. These Categories, span a wide and very inclusive range, some examples of the categories are: Fast-Food, Mexican, Italian, Steak-House, Asain-Cusine, SeaFood, etc. In a sense, this <code>numCategories</code> variable quantifies the versatility of a given restaurant. Thus, given a restaurant high versatility, it is not unreasonable to think, such a restaurant would have wide appeal, and this might manifest in the ratings. Thus we take a look at the following 

